\chapter{User Study of High-fidelity Prototype} \label{chap:user}
In the previous chapter, we created a HoloLens application to try out the most promising of our visualizations from the online survey in a more high-fidelity setting. In this chapter, we report how we use the application to conduct an informal user study. We have seven participants try out a range of visualizations, and we collect data by observing the participant's actions and by walking them through a prepared questionnaire. At the end of this chapter, we compare our earlier insights with this newly gathered information.

\section{Participants} \label{sec:user:survey:participants}
There were 7 unpaid male participants, 6 researchers and 1 student. All participants were familiar with the test environment, but none knew the corresponding lights for any specific switch in advance.

\section{Procedure} \label{sec:user:survey:procedure}
Each participant was received separately, with only the observer present. The participants were explained that the goal of the experiment was to evaluate various AR visualizations. They were given some time to adjust the HoloLens straps and get familiar with the device. Then we went over some steps to make sure the device was calibrated correctly and that the participants understood how to select switches. Finally we told them that they would be using six different visualizations to match lights and switches, and that each time they should think aloud as much as possible.

For each visualization, we told the participant the same words: ``Please select a switch, say which one you chose, then show which lights you believe are connected to it. Please try to think aloud as you decide''. We would note the participant's answer and whether it was correct. After each visualization, we asked the participant the same six 1-5 Likert scale questions about usability:
\begin{enumerate}
  \item How certain are you that the switches work the way you indicated?
  \item How ... do you find the visualization?
  \begin{enumerate}
    \item easy to learn
    \item fast to work with
    \item resistant to errors
    \item useful
    \item enjoyable
  \end{enumerate}
\end{enumerate}

The questions formed a semi-structured interview, rather than a base for statistical analysis, given the limited number of participants. We would ask the participants for the reasoning behind their scores, and if they saw ways to improve the visualizations. Throughout the entire process, we would note any interesting quotes, and also the participant's general behaviour for each visualization, like whether there were long periods of hesitation. After two or three visualizations, we would switch rooms, to introduce some variety and to avoid reusing switches.

Each participant received the same six visualizations, in the following orderwith slight variations in the order:
\begin{enumerate}
  \item World highlights
  \item Minimap highlights
  \item Wedges
  \item Halo's
  \item Combo (minimap highlights combined with wedges or halo's)
  \item Colors
\end{enumerate}

All participants started with the \textbf{world highlights}, which simply change the overlay color of lights from white to red. We considered them the most basic and recognizable visualization, since it has exactly the same effect as actually turning the lights on, but with the downside that the visualization does not radiate light from activated lamps, so users must look straight at them to be able to find them. With a total lack of overview and guidance, we did not consider this visualization an actual contender, at least not by itself. Rather, it was intended as a warm-up, and as a way of giving each participant the same reference point to compare the next visualizations to.

The second visualization for each participant was the \textbf{minimap highlights}, which showed a map of the participant's environment, on which lights would be highlighted in red, in the bottom right corner of their view. In contrast to the previous visualization, the minimap highlights do not require any head movement at all, once the user is acquainted with the environment. We placed this visualization second because maps are again a familiar concept that participants will be used to working with.

The third and fourth visualizations were the directional indicators. Half of the participants used the \textbf{wedges} first, the other half started with the \textbf{halo's}, so as to distribute the learning effect that these similar visualizations may have on each other. We followed up with the \textbf{combo} visualization, which is the minimap highlights combined with whichever of the two directional indicators the participant preferred. With this composite visualization, the participant had multiple ways of finding the correct lights, and we payed careful attention to which way they chose. This let us see how well their stated opinions and their actions lined up. We discussed with the participants whether the visualizations complemented each other, and we asked if they could think of better combinations.

The sixth last visualization for each participant were the \textbf{colors}. This visualization was placed last, because it functioned differently than the others, in the sense that no switch had to be selected. All circuits would be shown at once, each in their own color, both in the world and on the minimap. We pointed to several switches in quick succession and asked the participants to indicate the correct lights for each one. Each time we observed carefully whether the participants looked around, used the minimap, or both, and in what order. We finished with an open-ended discussion where we asked the participant's opinion of the entire concept and asked if they had any more insights to share.

\section{Apparatus} \label{sec:user:survey:apparatus}
Participants wore a HoloLens for the duration of the test, which was about 25 minutes. They used the accompanying clicker to select switches. The environment consisted of two office rooms with the adjacent hallway, and had 8 switches and 22 lights in total.

\section{Results} \label{sec:user:results}
There were 6 Likert scale questions for 6 visualizations, answered by 7 participants, which makes 42 trials and 252 scores in total, complemented with open questions. We will pay little attention to the scores, since they are inconclusive, and rather focus on the motivations that accompanied them. We can however note that all averages fell between 2.8/5 and 4.9/5, and that most scores were a 4+. We also note that some discussions were not in English. We have translated quotes from these conversations as literally as possible.

Across all 42 trials, 2 wrong answers were given. Both happened with the world highlights, but with different circuits. Both times the participant indicated there were two connected lights when there were actually three, because they missed a light that was hanging almost directly above them. Still, both participants were confident of their answer. In fact, the first question, ``How certain are you that the switches work the way you indicated?'', received a 5/5 in all but one case. Here the halo's received a 4, with the participant calling them ``... less precise because of the overlap. I prefer the wedges, those are more precise, smaller, they don't overlap as much.''.

Before going through the results of each visualizations, we believe it best to present the \textit{useful} and \textit{enjoyable} criteria separately. Most participants indicated they found these questions difficult to answer, especially the latter. Scores ranged widely, even within the same visualization. The negative opinions were mostly based on the HoloLens being unwieldy and having a small projection window, or on the presented problem being simple enough to solve by itself. One participant argued ``It's only lights, in this context nothing is dangerous, so it's not useful, in more complex scenarios it might be useful.'', while another explained that ``I wouldn't call this enjoyable. A football match I would call enjoyable, but turning on the lights I don't do for fun.''. When the scores were low because of the visualization itself, the scores for the other three criteria were also low.

For the \textbf{world highlights}, we observed all participants slowly looking around the room, until they came across the first red highlight, then quickly catching on and finding the other lights. All participants took 5-15 seconds to give their answer, and all described their thought process along the lines of ``I look around, I see red lights, the switch is also red, so these must belong together.''. The participants unanimously agreed the visualization was \textit{easy to learn}, but four participants had second thoughts on them being \textit{fast to work with} or \textit{resistant to errors}, stating that the visualization is ``... just as fast as simply trying out the switches.'' and that ``I can see myself miss a light from time to time.''.

For the \textbf{minimap highlights}, the minimap was not immediately noticed by one participant, who started looking around the room again. Two others saw the map but took some time to understand what it was. The remaining four participants gave the correct answer within seconds, and without looking up to do so, they simply pointed behind their backs. After realizing how the visualization worked, the other three were also quick to answer. Once having responded, four participants tried to confirm their answer by looking up to the lights as they had done previously, but of course there was nothing to see this time around. Six participants found the visualization very \textit{easy to learn}, but one described it as ``... harder than the other one.''. The criteria \textit{fast to work with} and \textit{resistant to errors} again received strong affirmation from all but one participant, who noted ``I think it's weird that part of the room is cut off, that feels like a bug. Some lights are almost cut away, ... but I can see the lights in the room next door, and those are not relevant.'' and ``The map is good for technical people, who are used to working with ground plans, I as an ordinary person don't have much experience with top-down views.".

Between the two directional indicators, five participants preferred the \textbf{wedges}, and two preferred the \textbf{halo's}. The general opinion is well described by this earlier mentioned quote, saying the halo's are ``... less precise because of the overlap. I prefer the wedges, those are more precise, smaller, they don't overlap as much.''. The two participants who preferred the halo's meanwhile argued they found the concept more familiar, and that in the wedges visualization, the purpose of what appeared to be half-open rectangles in the peripheral vision was not immediately clear. Opinions on all five criteria were mixed in both cases. One participant rated everything 4 or 5, while another maxed out at 3. We observed how four of the seven participants were initially confused by the visualizations, especially those who started with the halo's. In one extreme case, a participant who received the halo's first, needed multiple minutes before figuring out how the visualization worked. They described it as ``... randomly appearing lines, kind of a peripheral indication. I thought they were a representation of cables, that they were on the walls. After you understand it, it's still messy.'' They later nuanced their statement by putting some blame on the small rendering window of the HoloLens, and on implementation details, like the rate at which the circles expand and contract.

For the combo visualization, we observed every single participant answering using only the map. Two participants looked up after giving their answer to confirm what they had said, the other five didn't feel the need to do so, including the participant who earlier stated he found the map better suited for more technical people, and who gave the directional indicators only 4's and 5's. When asked how they would improve the combination, two participants wanted to remove the directional indicators, three suggested to make them optional, and the remaining two wanted to replace them with world highlights. All wanted to keep the minimap highlights.

Finally, for the colors visualization, where we asked to match several circuits that we pointed to in quick succession, all participants answered nearly instantaneously, and all used the map exclusively. When we pointed through the walls to switches in other rooms, the participants would still use the minimap if the lights fell within its range. Only when we purposefully pointed to a circuit outside the range of the minimap, did the participants look at the actual lights to determine their color. Even then, two participants felt the urge to walk up to the lights to get them in range of the minimap so they could confirm their answer. They said before doing so that they were confident of their answer, but they still wanted to verify it with the map. When we brought up this tendency to use the minimap with the participant who claimed the map was better for the technically inclined, they said they changed their opinion, and that they themselves now preferred the map, although they suspected directional indicators might still be helpful for beginners.

In our final open-ended discussion, all participants said the colors visualization was their favorite. An important reason for this that was repeatedly mentioned, was the fact that selection of switches was not needed when using the colors. Participants could answer all the questions without moving a finger. However, it was also repeatedly mentioned that they expected the colors to work less well in large or complex environments. Five of the seven participants could see themselves use the directional indicators in certain scenarios, specifically in ones with lights that are far away, so the minimap doesn't work as well, and where the lights spread out, so the indicators do not overlap too much.

\section{Discussion \& Conclusions} \label{sec:user:disc_conc}
Colors in both the real world and in the minimap appears to be an excellent general solution, since all participants liked it, were quick to pick it up, and could use it to work fast and without mistakes. When too many circuits are present to assign each of them a color, a combination of map highlights and and world highlights may work best. Then, the minimap can be used to locate the correct lights, and their redness allows the user to verify their assessment. When lights are really far away or spread out in different directions, directional indicators may be an effective tool for guiding the user's vision, or even for giving them a general sense of the layout.

The participants proposed many improvements, especially for the directional indicators:
\begin{itemize}
  \item Aiming at a switch and clicking is a bit cumbersome, ideally the user could scroll through the switches very quickly.
  \item Halo's might be clearer if their lines were thinner.
  \item Some participants experienced flickering or problems with depth vision, which may have inhibited the use of the visualizations.
  \item The wedges would be better if they used actual wedges, which remained completely within the user's vision, stuck to the periphery.
  \item Directional indicators should be replaced by world highlights once completely in sight.
  \item Halo's and wedges seem to grow too quickly, causing everything outside the user's vision to appear about the same distance away.
  \item The minimap can be a lot larger, it is no problem if it takes up a quarter or a third of the view, since it is transparent anyway.
  \item Users should be able to turn visualizations on and off at will.
  \item The minimap should zoom and/or shift so as to always encompass the current room or the currently selected circuit. The minimap could even pan away to far off lights, as long as this is done with the right animations, so that the user understands what is happening.
  \item When a circuit is selected, there should be an indication somewhere of how many lights in total are connected.
  \item If the user gazes over all selected lights, but misses one, the system could alert the user to this fact.
\end{itemize}

By implementing and evaluating these suggested improvements, we believe the effectiveness and the user-friendliness of our visualizations could be much improved. Especially the directional indicators currently appear to suffer from technical hamperings. Still, despite our prototype implementation, the participants were enthusiastic about its potential, and often spontaneously proposed ways to improve the system.
